Dynein walks like an Imperial AT-ST

### 2018-07-29 papers/paper/paper.tex
Add more descriptive caption to model figure

\begin{figure}[tbhp]
\includegraphics[width=0.5\linewidth]{../../plots/burgess-model-figure.pdf}%
%% \includegraphics[width=0.3\linewidth]{../../plots/redwine-model-figure.pdf}%
\includegraphics[width=0.5\linewidth]{../../plots/chowdhury-model-figure.pdf}\\
\includegraphics[width=0.5\linewidth]{../../plots/crystal-model-figure.pdf}%
\caption{\textbf{Hinge model compared with dynein micrographs.} \textit{Left:} Model superimposed over ---maybe the burgess paper is bad since it uses dynein c, which seems like an axonemal dynein}
\label{fig:duration-length}
\end{figure}

>>>>

\begin{figure}[tbhp]
\includegraphics[width=0.5\linewidth]{../../plots/burgess-model-figure.pdf}%
%% \includegraphics[width=0.3\linewidth]{../../plots/redwine-model-figure.pdf}%
\includegraphics[width=0.5\linewidth]{../../plots/chowdhury-model-figure.pdf}\\
\includegraphics[width=0.5\linewidth]{../../plots/crystal-model-figure.pdf}%
\caption{\textbf{Hinge model compared with dynein micrographs.} \textit{Green bg:} Model superimposed over an axonemal dynein micrograph consisting of an apo and and ADP-Pi-bound dynein monomer \cite{burgess-paper}. \textit{Grey bg:} Model superimposed over a native dynein micrograph \cite{nativestructure}. \textit{Black bg:} Model superimposed over crystal structures of two monomers, pink being the ADP-Pi-bound monomer (ID 4RH7), yellow being apo monomer (ID 3VKH), docked together using linkers as a reference point. Orange indicates the linker region used to dock the two monomers.}
\label{fig:duration-length}
\end{figure}
